---
output:
  html_document:
    theme: cerulean
    toc: true
    toc_float: false
    toc_depth: 3
---

<!-- Javascript for zooming on figures (adapted from: https://stackoverflow.com/questions/40401680) -->

<!-- Jquery import conflicts with DT::datatable so needs to be commented here -->
<!-- <script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script> -->

<style>
.zoomDiv {
  display: none;
  position: fixed;
  top: 50%;
  left: 50%;
  z-index: 50;
  transform: translate(-50%, -50%);
  background-color: #FFFFFF;
  box-shadow: 0px 0px 50px #888888;
  width: fit-content;
  max-width: 90%;
  max-height: 90%;
  overflow: auto;
}

.zoomImg {
  width: 100%;
}
</style>

<script type="text/javascript">
  $(document).ready(function() {
    $('body').prepend("<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>");
    // onClick for all img except the zoomed one and link ones (filter)
    // use 'img.zoom' and out.extra='class=\"zoom\"' in chunk to specify manually which chunk images can be zoomed
    $('img:not(.zoomImg)').filter(':not(a *)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src'));
      $('.zoomDiv').show();
    });
    // onClick function for hiding div
    $('img.zoomImg').click(function() {
      $('.zoomDiv').hide();
    });
  });
</script>

```{r rmd_setDynamicWidgetsOptions, include=FALSE}
# Set the use of multiple cores using 'future' library, as implemented in Seurat3 when possible
# https://github.com/satijalab/seurat/issues/457
#plan(strategy = "multicore", workers = NBCORES);

# Create a hidden plotly in a tagList to allow using them in loops later
cat('<div style="display: none">');
htmltools::tagList(plotly::plot_ly(x = rnorm(10), type = "histogram"))
cat('</div>');

# Same for datatable....
cat('<div style="display: none">');
DT::datatable( data.frame(a=1:10, b = 1:10),
           class = "compact",
           filter="top",
           rownames = FALSE,
           #colnames = ,
           #caption = ,
           extensions = c('Buttons', 'Select'))
cat('</div>');
```


```{r rmd_setKnitrOptions, include=FALSE}
# Set hook for PNG optimization ('optipng' must be installed on system)
#knitr::knit_hooks$set(optipng = knitr::hook_optipng)

# Set chunks default options
knitr::opts_chunk$set(results='asis',
                      echo = FALSE,           # Do not show chunks code
                      message = FALSE,        # Hide R regular text output in reports
                      warning = FALSE,        # Show warning messages
                      error = TRUE,           # Do not stop generating report on errors
                      cache = FALSE,          # Disable chunk result caching
                      cache.comments = FALSE, # Changing comments does not invalidate cache
                      fig.dim = c(5, 5),      # Size of device for R figures
                      autodep = TRUE,         # Automatic chunk dependencies if cache enabled
                      optipng = '-o2');       # PNG optimization level (2=default, 5=slow, 7=very slow)
```




```{r rmd_loadParamsAndDependencies, warning=FALSE, cache = FALSE}
### Define working folder
WORKING_DIR   = getwd();


### Load libraries, global functions/variables, and chunks
source( file.path( WORKING_DIR, "00_generalDeps.R"));

# Import chunks from source files
read_chunk( path=file.path( WORKING_DIR, "01_prepareData.R"));
read_chunk( path=file.path( WORKING_DIR, "02_variableGenes.R"));
read_chunk( path=file.path( WORKING_DIR, "03_cellHeterogeneity_PCA.R"));
read_chunk( path=file.path( WORKING_DIR, "04_cellHeterogeneity_UMAP.R"));
read_chunk( path=file.path( WORKING_DIR, "05_cellHeterogeneity_Clustering.R"));
read_chunk( path=file.path( WORKING_DIR, "06_cellTypeIdentification_Azimuth.R"));
read_chunk( path=file.path( WORKING_DIR, "07_cellTypeIdentification_MarkerGenes.R"));
read_chunk( path=file.path( WORKING_DIR, "08_cellTypeIdentification_ModuleGenes.R"));
read_chunk( path=file.path( WORKING_DIR, "90_finalize.R"));
```




---
title: `r paste( GLOBAL_DESCRIPTION, ANALYSIS_STEP_NAME, SAMPLE_NAME, sep ="<BR>")`
---




```{r rmd_initFunctions}

### Create output directory
dir.create( PATH_ANALYSIS_OUTPUT, recursive = TRUE, showWarnings = FALSE);
PATH_ANALYSIS_EXTRA_OUTPUT = file.path( PATH_ANALYSIS_OUTPUT, "Extra")
dir.create( PATH_ANALYSIS_EXTRA_OUTPUT, showWarnings = FALSE);


### Record starting time (for report and file names)
startTime = Sys.time();
startTimeReport   = format( startTime, "%Y %m %d %H:%M:%S")
startTimeFileName = format( startTime, "%Y_%m_%d_%H_%M_%S")


### Initialize utils

# Create a hash for all parameters
paramsHash = digest( environment(), algo="murmur32");

# Create a 'safe' unique prefix for output files (now specified at project scale in globalParams.R)
#outputFilesPrefix = path_sanitize( gsub("([[:punct:]])|\\s+",
#                                        "_",
#                                        paste0(PROJECT_NAME, "_",
#                                               SAMPLE_NAME, "_",
#                                               startTimeFileName, "_",
#                                               paramsHash, "_")),
#                                   replacement = "_");

# Set seed for pseudo random number generator
set.seed(SEED);

# Set the use of multiple cores using 'future' library, as implemented in Seurat3 when possible
# https://github.com/satijalab/seurat/issues/457
plan(strategy = "multicore", workers = NBCORES);

```




# Primary analysis (QC)




## Run informations {.tabset .tabset-fade}

### Run
<center>
```{r rmd_runInfo_run}
pander( c( 'Date'     = startTimeReport,
           'Sample'   = EXPERIMENT_NAME,
           'Hash'     = paramsHash));
```
</center>

### Parameters
```{r rmd_runInfo_params}
listParams = as.list( paramsEnv);
pander(listParams[order(names(listParams))]); # Show params in alphabetical order
```

### System
<center>
```{r rmd_runInfo_sysInfo}
showSimpleDT( Sys.info())
```
</center>

### R
```{r rmd_runInfo_r}
pander( sessionInfo());
```

<!-- Ending the tabset section -->
## {.toc-ignore}
<br /><br />


## Integration of samples

```{r rmd_dataLoad, warning = FALSE, fig.dim = c(9,6)}
<<loadData>>
```


## Filter and Normalize
```{r rmd_filter_and_normalize, warning = FALSE, fig.dim = c(7,5)}
<<filterData_selection>>
<<filterData_summaryPlot>>
<<filterData_filterObject>>
<<detect_doublet>>
<<normalizeData>>
```


## Detect variable genes
```{r rmd_variable_genes, warning = FALSE, fig.dim = c(7,5)}
<<findVariableGenes_seuratMethod>>
<<findVariableGenes_summaryPlot>>
<<findVariableGenes_summaryTable>>
```


## Dimensionality reduction : PCA
```{r rmd_dimentionality_reduction_pca, warning = FALSE, fig.dim = c(7,5)}
<<heterogeneity_pca>>
<<heterogeneity_pca_umisCounts>>
<<heterogeneity_pca_genesCounts>>
<<heterogeneity_pca_correlations>>
<<heterogeneity_pca_loadings>>
```


## Dimensionality reduction : UMAP
```{r rmd_dimentionality_reduction_umap, warning = FALSE, fig.dim = c(9,6)}
<<heterogeneity_dimReduc>>
<<dimreduc_ggplot_covariables>>
<<dimreduc_ggplot_doublets>>
```

## Analyse clustering {.tabset .tabset-fade}
```{r rmd_clustering, warning = FALSE, fig.dim = c(9,6)}
<<heterogeneity_identifyClusters_makeClusters>>
<<heterogeneity_identifyClusters_splitStats>>
<<dimreduc_ggplot_doublets>>
```


## Analyse cell type by Azimuth
```{r rmd_azimuth, warning = FALSE, fig.dim = c(9,6)}
<<heterogeneity_Azimuth>>
```

## Analyse cell type by Marker Genes {.tabset .tabset-fade}
```{r rmd_marker_genes, warning = FALSE, fig.dim = c(9,9)}
<<heterogeneity_markerGenes>>
<<heterogeneity_markerGenes_table>>
<<heterogeneity_markerGenes_heatmap_mean>>
```

```{r rmd_marker_genes_projection, warning = FALSE, fig.dim = c(4, 4), out.width='25%'}
<<heterogeneity_markerGenes_expression_projection>>
```

```{r rmd_marker_genes_violin, warning = FALSE, fig.dim = c(4, 4), out.width='25%'}
<<heterogeneity_markerGenes_expression_violin>>
```

## Analyse cell type by Gene Modules {.tabset .tabset-fade}

```{r rmd_heterogeneity_modules}
<<heterogeneity_modules>>
<<heterogeneity_modules_scoring>>
```

### Modules scoring heatmap

```{r rmd_heterogeneity_modules_heatmap, fig.dim = c(8, min(1+(length(MODULES_GENES)/10), 150))}
<<heterogeneity_modules_heatmap>>
```

### Modules scoring {.tabset .tabset-fade}

#### UMAP {.tabset .tabset-fade .tabset-pills}
```{r rmd_heterogeneity_modules_expression_projection_UMAP, fig.dim = c(4, 4), out.width='25%'}
cat("\n<a href='#clusters-projection'>");
cat("</a> \n \n");
<<heterogeneity_modules_expression_projection>>
```

#### Clusters violin {.tabset .tabset-fade}
```{r rmd_heterogeneity_modules_expression_violin, fig.dim = c(4, 4), out.width='25%'}
cat("\n<a href='#clusters-projection'>");
cat("</a> \n \n");
<<heterogeneity_modules_expression_violin>>
```

```{r rmd_final_saveSessionImage}
<<final_saveSessionImage>>
```


